Project Light

### 2015-09-09 paper/paper.tex
change screenshot to show only Android app

\begin{figure}
	\centering
	\includegraphics[scale=.35]{images/screenshots.png}
	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
	\label{fig:screenshots}
\end{figure}

@@

Hence, we built a native Android application written in Java.
Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing errors do not add up.
In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
% , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
Another advantage of this version is the flash light.
Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
Especially when attempting to program multiple motes at once this comes very handy.
To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.

>>>>

\begin{figure}
	\centering
	\includegraphics[scale=.15]{images/screen_native.png}
	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.}
	\label{fig:screenshot}
\end{figure}

@@

Hence, we built a native Android application written in Java.
Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing errors do not add up.
In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
% , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
Another advantage of this version is the flash light.
Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
Especially when attempting to program multiple motes at once this comes very handy.
To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshot}.
